Competing Bandits: The Perils of Exploration under Competition

### 2018-09-06 paper/content/barriers.tex
Moved the "barriers" table back to the "barriers" section.

>>>>

\begin{table*}[t]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
\hline
  & \multicolumn{3}{c||}{Reputation advantage}
  & \multicolumn{3}{c|}{Data advantage}\\
\hline
& $\TS$  & $\DEG$  & $\DG$
& $\TS$  & $\DEG$  & $\DG$
\\\hline
$\TS$
    & \makecell{\textbf{0.021}$\pm$0.009}
    & \makecell{\textbf{0.16}$\pm$0.02}
    & \makecell{\textbf{0.21} $\pm$0.02}
    %%
    & \makecell{\textbf{0.0096}$\pm$0.006}
    & \makecell{\textbf{0.11}$\pm$0.02}
    & \makecell{\textbf{0.18}$\pm$0.02}
    \\ \hline
$\DEG$
    & \makecell{\textbf{0.26}$\pm$0.03}
    & \makecell{\textbf{0.3}$\pm$0.02}
    & \makecell{\textbf{0.26}$\pm$0.02}
    %%
    & \makecell{\textbf{0.073}$\pm$0.01}
    & \makecell{\textbf{0.29}$\pm$0.02}
    & \makecell{\textbf{0.25}$\pm$0.02}
    \\ \hline
$\DG$
    & \makecell{\textbf{0.34}$\pm$0.03}
    & \makecell{\textbf{0.4}$\pm$0.03}
    & \makecell{\textbf{0.33}$\pm$0.02}
    %%
    & \makecell{\textbf{0.15}$\pm$0.02}
    & \makecell{\textbf{0.39}$\pm$0.03}
    & \makecell{\textbf{0.33}$\pm$0.02}
    \\\hline
\end{tabular}
\caption{Data advantage vs. reputation advantage experiment, on Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the {\bf row}) and the incumbent's algorithm (the {\bf column}). The cell specifies the entrant's market share for the rounds in which hit was present: the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\label{barrier_exp}
\end{table*}

### 2018-09-06 paper/content/inverted_u.tex
Removed a redundant line in a table.
Moved the "barriers" table back to the "barriers" section.

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Uniform} \\
\hline
   & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\ \hline
\TS vs \DG
  & \makecell{\textbf{0.46} $\pm$0.03}
    & \makecell{\textbf{0.52} $\pm$0.02}
    & \makecell{\textbf{0.6} $\pm$0.02} \\ \hline
\TS vs \DEG
    & \makecell{\textbf{0.41} $\pm$0.03}
    & \makecell{\textbf{0.51} $\pm$0.02}
    & \makecell{\textbf{0.55} $\pm$0.02} \\ \hline
\DG vs \DEG
    & \makecell{\textbf{0.51} $\pm$0.03}
    & \makecell{\textbf{0.48} $\pm$0.02}
    & \makecell{\textbf{0.45} $\pm$0.02} \\\hline
\end{tabular}
\caption{{\bf Permanent duopoly}, for the Uniform MAB instance. Semantics are the same as in Table \ref{sim_table}.}
\label{tab:duopoly_unif}
\end{table}

@@

\begin{table*}[ht]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
\hline
  & \multicolumn{3}{c||}{Reputation advantage}
  & \multicolumn{3}{c|}{Data advantage}\\
\hline
& $\TS$  & $\DEG$  & $\DG$
& $\TS$  & $\DEG$  & $\DG$
\\\hline
$\TS$
    & \makecell{\textbf{0.021}$\pm$0.009}
    & \makecell{\textbf{0.16}$\pm$0.02}
    & \makecell{\textbf{0.21} $\pm$0.02}
    %%
    & \makecell{\textbf{0.0096}$\pm$0.006}
    & \makecell{\textbf{0.11}$\pm$0.02}
    & \makecell{\textbf{0.18}$\pm$0.02}
    \\ \hline
$\DEG$
    & \makecell{\textbf{0.26}$\pm$0.03}
    & \makecell{\textbf{0.3}$\pm$0.02}
    & \makecell{\textbf{0.26}$\pm$0.02}
    %%
    & \makecell{\textbf{0.073}$\pm$0.01}
    & \makecell{\textbf{0.29}$\pm$0.02}
    & \makecell{\textbf{0.25}$\pm$0.02}
    \\ \hline
$\DG$
    & \makecell{\textbf{0.34}$\pm$0.03}
    & \makecell{\textbf{0.4}$\pm$0.03}
    & \makecell{\textbf{0.33}$\pm$0.02}
    %%
    & \makecell{\textbf{0.15}$\pm$0.02}
    & \makecell{\textbf{0.39}$\pm$0.03}
    & \makecell{\textbf{0.33}$\pm$0.02}
    \\\hline
\end{tabular}
\caption{Data advantage vs. reputation advantage experiment, on Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the {\bf row}) and the incumbent's algorithm (the {\bf column}). The cell specifies the entrant's market share for the rounds in which hit was present: the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\label{barrier_exp}
\end{table*}

>>>>

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|}
 % \hline
 % & \multicolumn{3}{c|}{Uniform} \\
\hline
   & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\ \hline
\TS vs \DG
  & \makecell{\textbf{0.46} $\pm$0.03}
    & \makecell{\textbf{0.52} $\pm$0.02}
    & \makecell{\textbf{0.6} $\pm$0.02} \\ \hline
\TS vs \DEG
    & \makecell{\textbf{0.41} $\pm$0.03}
    & \makecell{\textbf{0.51} $\pm$0.02}
    & \makecell{\textbf{0.55} $\pm$0.02} \\ \hline
\DG vs \DEG
    & \makecell{\textbf{0.51} $\pm$0.03}
    & \makecell{\textbf{0.48} $\pm$0.02}
    & \makecell{\textbf{0.45} $\pm$0.02} \\\hline
\end{tabular}
\caption{{\bf Permanent duopoly}, for the Uniform MAB instance. Semantics are the same as in Table \ref{sim_table}.}
\label{tab:duopoly_unif}
\end{table}

@@
